---
title: "Store24(A)"
author: "Roopak Krishna"
date: "15 January 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Task 4c

```{r,warning=FALSE,message=FALSE}
library(psych)
store <- read.csv(paste("Store24.csv",sep=""))
summary(store) # Summary statistics of Store24(A)
describe(store) 
```

#Task 4d

Measure the mean and standard deviation of Profit.
Measure the mean and standard deviation of MTenure.
Measure the mean and standard deviation of CTenure.


```{r,warning=FALSE,message=FALSE}
meanresult <- apply(store[,3:5],2,mean)
meanresult   # mean of Profit, MTenure, CTenure

sdresult <- apply(store[,3:5],2,sd)
sdresult                                # standard deviation of Profit, MTenure, CTenure
```

#Task 4f

Print the {StoreID, Sales, Profit, MTenure, CTenure} of the top 10 most profitable stores.

```{r,warning=FALSE,message=FALSE}
store.sub <- subset(store, select=c(1:5))
newstore <- store.sub[order(-store.sub$Profit),]
newstore[1:10,]
```

Print the {StoreID, Sales, Profit, MTenure, CTenure} of the bottom 10 least profitable stores.

```{r,warning=FALSE,message=FALSE}
newstore <- store.sub[order(store.sub$Profit),]
newstore[1:10,]
```

#Task 4g


Draw a scatter plot of Profit vs. MTenure.


```{r,warning=FALSE,message=FALSE}
library(car)
scatterplot(store$MTenure,store$Profit,main="Scatterplot of Profit vs MTenure",xlab="MTenure",ylab="Profit",smoother=loessLine,smooth = TRUE, span =0.5,smoother.args=list(lty=2),spread=FALSE )

```

#Task 4h

Draw a scatter plot of Profit vs. CTenure

```{r,warning=FALSE,message=FALSE}
scatterplot(store$CTenure,store$Profit,main="Scatterplot of Profit vs CTenure",xlab="CTenure",ylab="Profit",smoother=loessLine,smooth = TRUE, span =0.5,smoother.args=list(lty=2),spread=FALSE )

```

#Task 4i

Construct a Correlation Matrix for all the variables in the dataset. (Display the numbers up to 2 Decimal places).

```{r,warning=FALSE,message=FALSE}
round(cor(store),2)
```

#Task 4j

Measure the correlation between Profit and MTenure. (Display the numbers up to 2 Decimal places)

```{r,warning=FALSE,message=FALSE}
round(cor(store$Profit,store$MTenure),2)
```

Measure the correlation between Profit and CTenure.  (Display the numbers up to 2 Decimal places)

```{r,warning=FALSE,message=FALSE}
round(cor(store$Profit,store$CTenure),2)
```

#Task 4k

Construct the Corrgram based on all variables in the dataset.

```{r,warning=FALSE,message=FALSE}
library(corrgram)
corrgram(store, main="Corrgram of Store Variables", lower.panel=panel.shade, 
         upper.panel=panel.pie, text.panel=panel.txt)
```

#Task 4l

Run a Pearson's Correlation test on the correlation between Profit and MTenure. What is the p-value?

```{r,warning=FALSE,message=FALSE}
cor.test(store$Profit, store$MTenure)
```

p-value = 8.193e-05


Run a Pearson's Correlation test on the correlation between Profit and CTenure. What is the p-value?

```{r,warning=FALSE,message=FALSE}
cor.test(store$Profit, store$CTenure)
```

p-value = 0.02562


#Task 3m

Run a regression of Profit on {MTenure, CTenure Comp, Pop, PedCount, Res, Hours24, Visibility}.

```{r,warning=FALSE,message=FALSE}
regression.store <- lm(Profit ~ MTenure + CTenure + Comp + Pop + PedCount + Res + Hours24 + Visibility,data =store)
summary(regression.store)
```

#Task 4n

List the explanatory variable(s) whose beta-coefficients are statistically significant (p < 0.05).

```{r,warning=FALSE,message=FALSE}
summary(regression.store)$coefficients[summary(regression.store)$coefficients[,4] <=0.05,4]
```

List the explanatory variable(s) whose beta-coefficients are not statistically significant (p > 0.05).

```{r,warning=FALSE,message=FALSE}
summary(regression.store)$coefficients[summary(regression.store)$coefficients[,4] > 0.05,4]
```

#Task 4o

What is expected change in the Profit at a store, if the Manager's tenure i.e. number of months of experience with Store24, increases by one month?

```{r,warning=FALSE,message=FALSE}
summary(regression.store)$coefficients["MTenure",1]
```


What is expected change in the Profit at a store, if the Crew's tenure i.e. number of months of experience with Store24, increases by one month?

```{r,warning=FALSE,message=FALSE}
summary(regression.store)$coefficients["CTenure",1]
```

#Task 4p

The Insights drwan from this analysis is :-

1. Profits of a store depends on both MTenure and CTenure but MTenure has more effect on Profits comparatively to CTenure.
2. From corrgram, 24 hour opened store doesn't lead to much profit.
3. From regression analysis :-
   - MTenure, comp, Pedcount is more significant (3 star).
   - Hours 24 is also a significant variable (2 star).
   - CTenure, Pop, Res is also a significant variable (1 star).
   - Visibility is not a significant variable.
4. The multiple r-squared value is 0.6379 that means that 63.79% of the variance in the response that is explained by Predictors.